---
title: "Predicting organic installs multiplier"
author: "Samuel Chan"
date: "24 April 2017"
output:
  pdf_document: default
  html_document: default
---

This exercise is motivated by a request from an industry friend, who is interested to learn the **organic multiplier** rate for mobile app campaigns in the Shopping category in an unspecified geo / country. 

*Some initialization and configuration*
```{r}
# clear our global environment
rm(list=ls())

# effectively prevent scientific notation e.g e+04
options(scipen = 999)
```

### Read in the data and simple exploratory
```{r}
# Read in the data
data <- read.csv("data2.csv", header=TRUE)

# Feature construction
data$total <- data$paid + data$organic

# Examine if there is a fairly linear relationship between paid and organic
library(ggplot2)
ggplot(data = data, aes(x=paid, y=organic))+geom_point()+labs(x="Paid installs", y="Organic Installs", main="Paid vs Organic installs")+geom_smooth(method=lm)
```
Notice our use of `method=lm` automatically assume a 95% confidence region


### Fit our first linear regression line
```{r}
fit <- lm(organic ~ paid, data = data)
summary(fit)
```
Interpreting the outlut: Values of coefficients are 1072240 and 1.462, hence prediction equation for model using the provided dataset is as below:
**Organic installs = 1072240 + 1.462 * paid installs**

We also observed that our _cost_ is 933400 (residual standard error)

# Compare organic installs predicted by the linear regression model vs actual values
```{r}
actual.o <- data$organic
pred.o <- fitted(fit)
comparison <- as.data.frame(cbind("Actual Organic"=actual.o, "Predicted Organic" = pred.o, "Difference (%)" = round(sqrt((actual.o-pred.o)^2)/actual.o*100, 2)))
comparison[1:25,]
```
Our formula here: **Organic installs = 1072240 + 1.462 * paid installs** can quite reliably predict the organic installs of many days with roughly 2% to 8% of error (difference). Depending on your use-case, this may or may not be a sufficient predictive model. There were 2 days of outlier (21st March and 22nd March respectively), but those are likely the result of extra boost campaign unaccounted in the data -- or possibly an Apple AppStore feature or Google Play feature.

### If we have removed the outlying 21st and 22nd March's data
```{r}
data2 <- data[-c(21,22),]
fit2 <- lm(organic ~ paid, data = data2)
summary(fit2)
```
We would achieve a multiple R-squared value of ~0.7.


### Caveat
It is important to note here that the dependent variable (organic installs / multiplier) is correlated with the independent variable (paid installs) but this correlation do not imply causation. That is, as the number of paid installs changes, we observe a change in the organic installs. This should not be inferred or interpreted to mean that the paid installs has _caused_ the number of organic installs to change.

However, we should also note that the model has a multiple R-squared value of *0.6956*. An easy way to intepret this is that the linear model as a whole explains nearly 70% of the variation in our dependenable variable. We have after all, fit a simple linear model and this exercise should in no way be considered robust or scientifically rigorous. To improve our model's performance, we could:

- Obtain larger datasets  
- Construct multiple features on each observation (app's placement on top free download rankings, top free shopping rankings)
- Variability (datasets spanning across multiple months)  

We should also acknowledge that a game or mobile app's inherent design, including its virality features, social features, in-game social gifting features etc might also a role in the organic multiplier. Obtaining bigger sample sizes or more data could help in our hypothesis design. 

Despite its simplicity, we also observe that a linear model is powerful enough as a predictor for organic multiplier on the provided data, and has the added advantage of being effective despite the relatively small sample size. 



